The Astropy Project

### 2017-11-10 main.tex
edit constants

\subsection{Constants}

%David S.

The \package{Constants} package provides a selection of physical and astronomical
constants as quantities.  A brief description was given in \cite{astropy}.
For version 2.0, constants have been organized into modules for specific versions.
Physical constants include \texttt{codata2014} \citep{codata2014}
and \texttt{codata2010} versions. Astronomical constants are organized
into \texttt{iau2015} and
\texttt{iau2012} modules to roughly indicate their sources.
The \texttt{codata2014} and \texttt{iau2015} versions are combined
into the default \texttt{astropyconst20}
version. For astropy v1.3 and earlier, the \texttt{astropyconst13}
namespace is available;
however when using previous versions of the constants,
\package{Constants} should be used
directly, since  \package{astropy.units} will be initialized to the
\texttt{astropyconst20} versions.

Astronomers using \package{Constants} should take particular note of the
constants provided for Earth, Jupiter and the Sun. Following IAU 2015
Resolution B3 \citep{iau2015b3}, nominal
values are now given for mass parameters and radii. The nominal values
will not change even as ``current best estimates'' are updated.

>>>>

\subsection{Constants}
% David S.
% Edited by Adrian PW

The \texttt{astropy.constants} subpackage provides a selection of physical and
astronomical constants as \texttt{Quantity} objects (see
\sectionname~\ref{sec:units}).
A brief description of this package was given in \citep{astropy}.
In version 2.0, the built-in constants have been organized into modules for
specific versions of the constant values.
For example, physical constants have \texttt{codata2014} \citep{codata2014} and
\texttt{codata2010} versions.
Astronomical constants are organized into \texttt{iau2015} and \texttt{iau2012}
modules to indicate their sources (resolutions from the International
Astronomical Union, IAU).
The \texttt{codata2014} and \texttt{iau2015} versions are combined into the
default constant value version: \texttt{astropyconst20}.
For compatibility with \astropypkg version 1.3 and earlier, the \texttt{astropyconst13}
namespace is still available and provides access to the adopted versions of the
constants from earlier versions of \astropypkg.
To use previous versions of the constants as \emph{units} (e.g., solar masses),
the values from the desired namespace have to be imported directly; with version
2.0, \texttt{astropy.units} uses the \texttt{astropyconst20} versions.

Astronomers using \texttt{astropy.constants} should take particular note of the
constants provided for Earth, Jupiter, and the Sun.
Following IAU 2015 Resolution B3 \citep{iau2015b3}, nominal values are now given
for mass parameters and radii.
The nominal values will not change even as ``current best estimates'' are
updated.
